\begin{acknowledgements}


    First and foremost, I would like to express my deepest gratitude to my supervisor Bryan Ruddy and Andrew Taberner, who have provided me with the opportunity and a tremendous amount of support to allow me to complete my Ph.D. work at the ABI. They have dedicated much time and hands-on effort, including the time spent outside of their office hours in the last four years.
    
    
    My special thanks are going to Dr. Bryan Ruddy. I am very
    grateful to have had Bryan as a main supervisor, who has not only encouraged me to develop new skills but also spent time to teach me specialized subjects. He possesses an incredible depth of knowledge on a wide range of subjects, a very generous amount of compassion and a talent for baking. There were not just once when life got hard and confusing to the point that I considered suspending, but his encouragement and advice stayed with me and allowed me to push through. Bryan has also given me an incredible degree of flexibility during my Ph.D., which allowed me to travel extensively, learn more about the world, take on entrepreneurship activities, and truly grow beyond my old self.
    
    
    Associate Professor Andrew Taberner has been a key mentor and guide for me throughout my journey. Andrew has the rare talent of connecting seemingly unrelated principles to constantly produce new and original ideas. I am thankful for such a resourceful and passionate supervisor who has helped me navigate through my Ph.D.
    
    
    I would like to extend my appreciation toward Professor Poul Nielsen, as a leading member of the Jet Injection group who has offered me with his sharp and constructive criticism. His assistance and advice have been helpful to me in this degree.
    
    
    I would like to thank the ABI Bioinstrumentation lab as a great place for me to complete my Ph.D. Thank you, Dr. James McKeage, Dr. Kieran Brennan, Jiali Xu for teaching me and helping me navigate through our existing Needle-free Injection infrastructure. I would like to acknowledge Patrin Illenberger, Dr. Duleepa Thrimawithana, and Greg Dawick who have given me a tremendous amount of help for my power electronics work. A special thanks to Stephen Olding who allowed me to collaborate on the manufacturing process of high spec mechanical parts in my Ph.D. Callum Walley was the person who taught me neat tips and tricks on how to fully utilize the HPC resource that I was lucky enough to interact with. I could not have completed all the work in my Ph.D. without all of you. 
    
    
    I owe a lot of the enjoyable time working in the ABI to Sorosh Hosseinnejad, Dr. James McKeage, Dr. Kieran Brennan, Jiali Xu, Dr. Toan Pham, Bahareh Madadkhahsalmassi, Dr. Paul Roberts, Sam Richardson, Alex Dixon, Jarrah Dowrick, Patrin Illenberger, Alistair Newcombe, Hayden Randles, Emily Lam Po Tang, Kevin Choi, Jarrah Dowrick, Amy Garrett, Greg Dawick, Dr. JC Han, Associate Professor Loiselle, Yahya Yahya, Mahsa Momtahan, and Stephen Olding. It has been a lot much fun working with these people and all of our discussions have helped me greatly over the years. I would like to also thank the "old boys" of the ABI: Dr. Ming Cheuk, Dr. Daniel Chen, Dr. Matt Parker, and Dr. Amir Hajirassouliha. The "old boys" have left me with valuable advice on how to gain the most out of doing a Ph.D. The ABI staff Nancy Wong, Carmen Balanon, Kosala Krishnan, Nora Garcia-Mora, Nina Pettersson-Fox, Dr. Diana Siew and Kelly Diep have been very supportive and helpful. The honorable mentions are for Dr. KJ Wang and Oliver Lin. The time that I worked in the ABI will always be treasured.
    
    
    I would also like to thank the organizations who financially supported my study and allowed me to pursue this Ph.D. degree: The University of Auckland, The Auckland Bioengineering Institute, and The MedTech Centre of Research Excellence. 
    
    
    I would like to acknowledge the New Zealand eScience Infrastructure (NeSI) for my rare chance to gain experience in HPC, as well as about 500,000 worth of single-core compute hours, a mail server crash incidence, and a couple of HPC reboots.
    
    
    I am very grateful to you as my mentors outside of the university environment: Dr. Minh Nguyen, Doyle Trinh, Alan Faull, Andreas Mueller, Nghia Nguyen, Yukio Fukuzawa, and Kevin Tran. 
    
    
    Thank you for the emotional support from my friends Mark Do, Hung Do, Tung Nguyen, Tom Nguyen, and Dr. Andy Nguyen. The time I had with my friends outside of work including Richard Lee, Shaoqing Meads, Tommy Kim, Nikko Pham, Minh Dinh, Steve Tran, Marcus Leung, Minh Nguyen, Ngan Pham, Otari Beldishevski, Nicole Yip, Tai Nguyen, Viet Hoang, Dr. Tan Do, Thao Le, Tam Le, Hoang Le, Anh Phan, Tuan Dinh, Tram Dinh, Phong Nguyen, Tan Nguyen, Son Dinh, Vincent Ho, Long Dao, Bella Du, Sao Tran, Neil Ly, Dung Ta, and Jaydon Cheng was great fun. A very special thank is going to Vahe Singh, and because you, I will forever appreciate the freedom of choosing my own work.
    
    
    Thank you, Mum and Dad, for your unbounded love and support which allowed me to get this far in life. Thank you, my sister, Duong Do. I lost counts of the times when Duong took on little everyday tasks to support me when I was snowed under work. I am grateful to have a loving and supportive family. In particular, I would like to thank my wife Mai Le, who has been there and supported me through all the highs and lows of my Ph.D. time. I would not have made it without her love, care, and support. 
    
    
    I start this Ph.D. for myself alone, but I finish this all-rounded body of work with all of you on my mind.
    

\end{acknowledgements}